---
title: "Quality Control Case"
author: "ECM"
date: "4/6/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("car") # only do this once
library(car)   # do this every R session
#setwd("/Users/ecm/teach/data/")
#quality = read.csv("quality.csv")
quality = data.frame( temp=c(.97,2.85,2.95,2.84,1.84,2.05,1.5,2.48,2.23,3.02,2.69,2.63,1.58,2.48,2.25,
  2.76,2.36,1.09,2.15,2.12,2.27,2.73,1.46,1.55,2.92,2.44,1.87,1.45,2.82,1.74), density=c(32.08,21.14,20.65,22.53,27.43,25.42,27.89,23.24,23.97,19.45,23.17,
  22.7,27.49,24.07,24.38,21.58,26.3,32.19,25.73,25.18,23.74,24.85,30.01,
  29.42,22.5,23.47,26.51,30.7,22.3,28.47), rate=c(177.7,254.1,272.6,273.4,210.8,236.1,219.1,238.9,251.9,281.9,254.5,265.7,
  213.3,252.2,238.1,244.7,222.1,181.4,241,226,256,251.9,192.8,223.9,260.0,236,
  237.0,221,253.2,207.9), 
am=c(0,1,1,1,0,1,0,0,0,1,1,1,0,0,0,1,1,0,0,0,1,1,0,1,1,0,0,1,1,0), defect=c(.2,47.9,50.9,49.7,11,15.6,5.5,37.4,27.8,58.7,34.5,45,6.6,31.5,23.4,
  42.2,13.4,0,20.6,15.9,44.4,37.6,2.2,1.5,55.4,36.7,24.5,2.8,60.8,10.5) )
str(quality)
summary(quality)
```

# 1. Scatterplot matrix
```{r}
plot(quality, pch=16)
```

## 1b Correlation matrix
```{r}
round(cor(quality), 3)
```

# 2. Multiple regression
```{r}
fit = lm(defect~., quality)
summary(fit)
vif(fit) 
```
$H_0: \beta_1 = \beta_2 = \beta_3 = \beta_4 = 0$ 

$H_1:$ at least one $\beta_j\ne 0$, $j=1, 2, 3, 4$

$P=3.23 \times 10^{-11} \ll 0.05$ so we easily reject $H_0$. Which of the predictors is significant?

# 3. Simple linear regressions
## 3.1 Temperature
```{r}
summary(lm(defect~temp, quality))
```
## 3.2 Density
```{r}
summary(lm(defect~density, quality))
```
## 3.3 Rate
```{r}
summary(lm(defect~rate, quality))
```
## 3.4 AM
```{r}
summary(lm(defect~am, quality))
```

# 4. Further analysis
```{r}
summary(lm(defect~rate+am, quality))
```
# 5. Regression vs $t$ test
## 5.1 $t$ test
```{r}
t.test(defect~am, quality, var.equal=T)
```

## 5.2 Regression of defects on am
```{r}
summary(lm(defect~am, quality))
```
\[ \hat{y} = 16.92 + 20.44\textrm{am} \]

For am=0, $\hat{y} = 16.92$, which is the mean of pm from the $t$ test.

For am=1, $\hat{y} = 16.92 + 20.44 = 37.36$ which is the mean of am from the $t$ test.

The "slope" of 20.44 is the difference between the am and pm shifts! As the variable increases by 1 (i.e., pm to am) the change in defects is 20.44, on the average. This makes the meaning of dummies clear.